---
title: "RVTools VMWare Cluster Report"
author: "Kwan Lowe"
output: pdf_document
---

Report Date: `r format(Sys.Date(), format="%B %d %Y")`.

```{r, echo=FALSE}
 suppressMessages(library(lubridate))
 suppressMessages(library(dplyr))
 suppressMessages(library(gridExtra))
 suppressMessages(library(grid))
 
 clusterName <- "VMWareCluster"
 rvDataPath <- "rvtools/daily/"
 rvHostFile      <- paste0(rvDataPath, "RVTools_tabvHost.csv")
 rvMemoryFile    <- paste0(rvDataPath, "RVTools_tabvMemory.csv")
 rvDatastoreFile <- paste0(rvDataPath, "RVTools_tabvDatastore.csv")

 setwd("~/src/R/")

 if (file.exists(rvHostFile)){
   hostData <- read.csv(rvHostFile)
 }

 storageData <- read.csv(rvDatastoreFile)
 memoryData <- read.csv(rvMemoryFile)

 linuxClusterData <- filter(hostData, Cluster==clusterName) %>%
   select(Host, Speed, X..CPU, Cores.per.CPU, X..Cores, 
          CPU.usage.., X..Memory, Memory.usage.., VMs.per.Core,
          VM.Used.memory)
 
 linuxClusterData <- dplyr::rename(linuxClusterData, 
                                 Sockets = X..CPU,
                                 Cores.per.Socket=Cores.per.CPU,
                                 Cores = X..Cores,
                                 Cpu.Usage = CPU.usage.. ,
                                 Memory.Percentage=Memory.usage..,
                                 Host.Memory=X..Memory) 


 linuxMemoryData <- filter(memoryData, Cluster==clusterName) %>%
   select(VM, Size.MB, Overhead, Max, Consumed, Consumed.Overhead, Private, Active, Entitlement)

vmMemoryUsed <- sum(linuxMemoryData$Consumed)
hostMemory   <- sum(linuxClusterData$Host.Memory)
clusterMemory <- vmMemoryUsed/hostMemory

linuxStorage <- subset(storageData, grepl("Linux", storageData$Name))

linuxStorage <- storageData
storageTB <- round((sum(linuxStorage$Capacity.MB))/1024/1024)
provisionedTB <- round(sum(linuxStorage$Provisioned.MB)/1024/1024)
inUseTB <- round(sum(linuxStorage$In.Use.MB)/1024/1024)



```

Linux cluster memory capacity is currently at `r round(clusterMemory*100)`% utilization. 
There is `r round(hostMemory/1024)`GB available in the cluster, of which 
`r round(vmMemoryUsed/1024)`GB is in use.

Linux storage capacity is currently at `r storageTB `TB, of which 
`r provisionedTB`TB have been provisioned. There is `r inUseTB`TB in actual use.

There are `r sum(linuxClusterData$Cores)` cores in the cluster, of which 
`r sum(linuxClusterData$Cpu.Usage)` cores are allocated. There are 
an average of `r round(mean(linuxClusterData$VMs.per.Core), digits=2)` 
VM(s) per core. Average CPU usage at the time of this report is
`r round(mean(linuxClusterData$Cpu.Usage))`% for the cluster.

```{r, echo=FALSE}

mytheme <- gridExtra::ttheme_default(
    core = list(fg_params=list(cex = 0.8)),
    colhead = list(fg_params=list(cex = 0.8)),
    rowhead = list(fg_params=list(cex = 0.8)))

myt <- gridExtra::tableGrob(select(linuxClusterData, Host, Sockets, Cores, 
                                   Cpu.Usage, Memory.Percentage), theme = mytheme)

grid.draw(myt)
```
