---
title: "Summarizing AWS Data with R"
author: "Kwan Lowe"
date: "March 23, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summarizing AWS Data with R

Amazon Web Services (AWS) lets users spin up servers and storage in seconds. This can come at a cost.

Though there are many existing tools to query AWS data, this shows some quick ways in R to get AWS metrics such as total storage, amemory and CPU. 

### Show total storage for all volumes

The describe_volumes_out.json is the output from:
```
  aws ec2 describe-volumes --output=json
```
```{r summary_storage}
library(jsonlite)
library(varhandle)
library(xlsx)
volumes <- fromJSON("tmp/describe_volumes_out.json")

sum(volumes$Volumes$Size)
```

Finally, output to Excel for the PHBs.

```{r write_excel}
voldata <- cbind(volumes$Volumes$VolumeId, as.integer(volumes$Volumes$Size), volumes$Volumes$State)
colnames(voldata) <- c("VolumeId", "Size", "State")
voldata <- transform(voldata, Size = noquote(Size))
voldata <- unfactor(voldata)

write.xlsx(voldata, "tmp/volumedata.xlsx")

head(voldata)
```

## Graphing the data (IN PROGRESS)
