---
title: 'R for Sysadmins: WordClouds'
author: "Kwan Lowe"
date: "8/26/2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R for SysAdmins: WordClouds

A wordcloud is a PHB-friendly way to visualize where the hot areas are in your
problem ticket queue. More common words a printed in a larger font so it is 
easy to see systems that are generating tickets.

For this example, I exported my Remedy ticket queue to a CSV file. It required
some basic massaging to clean up Microsoft encoding and drop the mail headers.
That process, unfortunately, is out of scope for this demo. :)


```{r main, cache=TRUE}
library(tm)
library(SnowballC)
library(wordcloud)
```

This example is mostly verbatim from the R-bloggers example in the resources 
section. Main addition was to add some custom removed words. 


```{r readData, cache=TRUE}
mywords <- c("Kwan", "Lowe", "Management" )
remedy <- read.csv("remedy.csv", stringsAsFactors = FALSE)

remedyCorpus <- Corpus(VectorSource(remedy$Text))
remedyCorpus <- tm_map(remedyCorpus, PlainTextDocument)
remedyCorpus <- tm_map(remedyCorpus, removePunctuation)
remedyCorpus <- tm_map(remedyCorpus, removeWords, stopwords('english') )
remedyCorpus <- tm_map(remedyCorpus, removeWords, mywords )
wordcloud(remedyCorpus, max.words = 80, random.order = FALSE)
```

It may take a few minutes to run depending on the size of your dataset. 

My example datafile is somewhat noisy. If you wanted to use this process
in a production environment, you might consider using error codes or other
terms.


## References
[R-bloggers.com Article][https://www.r-bloggers.com/building-wordclouds-in-r/]

End.
